Rjags parameters

### 2020-09-14 Scripts/Rjags.tunning.Rmd
no site
Aaargg

for (i in 1:10){
  all.hashes <- model.round.nested(Nested.Hashes, n = i)
}
```

>>>>

Nested.Hashes %>% 
  mutate (susp = "Yes") %>% 
  nest(-susp) -> Nested.Hashes

for (i in 1:10){
  Nested.Hashes <- model.round.nested(Nested.Hashes, n = i)
}

write_rds(Nested.Hashes, here("Input", "Occupancy.nosite.rds"))

all.hashes <- read_rds(here("Input", "Occupancy.nosite.rds"))

all.hashes ->test
